Assessing Infant Mortality Rate: Problem stemming from Household Living Conditions, Women's Education and Health

### 2022-04-26 outputs/paper/paper.Rmd
update

---
title: "Assessing Infant Mortality Rate: Problem stemming from Household Living Conditions, Women's Education and Health"
subtitle: "Trends in India from the 1998 Demographic Health Survey"
author: 
  - Jacob Yoke Hong Si
thanks: "Code and data are available at: https://github.com/jacobyokehongsi/Assessing_the_Knowledge_of_AIDS_amongst_Women_in_1997_Vietnam"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "What areas of women's and children's health and living conditions can be improved in order to reduce the infant mortality rate? Utilizing the data from the 1998-1999 India National Family Health Survey provided by the Demographic and Health Survey (DHS) program, we look to depict the demographics of Indian Women and Children in different states of India. We found that the root cause of poor infant mortality rates stem from having poor living conditions. The living environment affects the likelihood of women to attain education and understand the importance of antenatal care. We also explore other factors such as inheritable traits (body weight and anaemia disease) as well as an infant's diet. These factors are crucial in the development of an infant and the reduction of the infant mortality rate. \\par \\textbf{Keywords:} health, living conditions, infant mortality rate, education, antenatal care, body weight, anaemia, diet"
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- The dataset has not been used for other tasks yet.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- TBD
3. *What (other) tasks could the dataset be used for?*
	- Tasks could include analyzing the demographics of women and children in India during 1998-1999.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- The preprocessing is curated just for this specific dataset and cannot be applied to other datasets.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- N/A
6. *Any other comments?*
	- N/A

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Jacob Yoke Hong Si
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- Through email at jacobyh.si@mail.utoronto.ca.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- There is no erratum.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- There is no plan to update the dataset. Any updates will be communicated to dataset consumers via Github.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- There are no applicable limits on the retention of the data associated with the instances.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions will not be hosted. Its obsolenscence is communicated via commit history on Github.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- The repository on Github can be cloned to extend/augment/build on/contribute to the dataset. Contributions will not be validated/verified since I am not responsible for any other dataset extensions. 
8. *Any other comments?*
	- N/A

>>>>

---
title: "Assessing Infant Mortality Rate: Problem stemming from Household Living Conditions, Women's Education and Health"
subtitle: "Trends in India from the 1998 Demographic Health Survey"
author: 
  - Jacob Yoke Hong Si
thanks: "Code and data are available at: https://github.com/jacobyokehongsi/Assessing_Infant_Mortality_Rate_in_1998_India"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "What areas of women's and children's health and living conditions can be improved in order to reduce the infant mortality rate? Utilizing the data from the 1998-1999 India National Family Health Survey provided by the Demographic and Health Survey (DHS) program, we look to depict the demographics of Indian Women and Children in different states of India. We found that the root cause of poor infant mortality rates stem from having poor living conditions. The living environment affects the likelihood of women to attain education and understand the importance of antenatal care. We also explore other factors such as inheritable traits (body weight and anaemia disease) as well as an infant's diet. These factors are crucial in the development of an infant and the reduction of the infant mortality rate. \\par \\textbf{Keywords:} health, living conditions, infant mortality rate, education, antenatal care, body weight, anaemia, diet"
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

@@

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- The dataset has not been used for other tasks yet.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- https://github.com/jacobyokehongsi/Assessing_Infant_Mortality_Rate_in_1998_India
3. *What (other) tasks could the dataset be used for?*
	- Tasks could include analyzing the demographics of women and children in India during 1998-1999.
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- The preprocessing is curated just for this specific dataset and cannot be applied to other datasets.
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- N/A
6. *Any other comments?*
	- N/A

@@

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Jacob Yoke Hong Si
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- Through email at jacobyh.si@mail.utoronto.ca.
3. *Is there an erratum? If so, please provide a link or other access point.*
	- There is no erratum.
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- There is no plan to update the dataset. Any updates will be communicated to dataset consumers via Github.
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- There are no applicable limits on the retention of the data associated with the instances.
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- Older versions will not be hosted. Its obsolescence is communicated via commit history on Github.
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- The repository on Github can be cloned to extend/augment/build on/contribute to the dataset. Contributions will not be validated/verified since I am not responsible for any other dataset extensions. 
8. *Any other comments?*
	- N/A
